JARINGAN DAN PENGOLAHAN DATA PARALEL

### 2021-12-31 Semester I/Jaringan dan Pengolahan Data Paralel/praktikum/Laporan Praktikum.Rmd
new

metode = c("Serial","Broadcast","Broadcast Gather","Broadcast Reduce",
	   "Gather","Multi Processing","Multi Threading","P2P")
nilai = c(0.33333333333331167,0.33333333333331167,0.3333333333333456,0.3333333333333455,
	  0.3333333333333456,0.33333333333333925,0.33333333333331167,NA)
runtime = c(27.43908143043518,56.21210050582886,6.989081621170044,7.089271306991577,
	   7.081090211868286,7.525770664215088,254.07278299331665,NA)
```

>>>>

metode = c("Serial","Broadcast","Broadcast Gather","Broadcast Reduce",
	   "Gather","Multi Processing","Multi Threading","P2P",
	   "Reduce","Scatter","Scatter Gather","Scatter Reduce")
nilai = c(0.33333333333331167,0.33333333333331167,0.3333333333333456,0.3333333333333455,
	  0.3333333333333456,0.33333333333333925,0.33333333333331167,0.333333333333333,
	  0.3333333333333455,0.33333333333331167,0.3333333333333456,0.3333333333333455)
runtime = c(27.43908143043518,56.21210050582886,6.989081621170044,7.089271306991577,
	    7.081090211868286,7.525770664215088,254.07278299331665,7.182239143,
	    7.1590189933776855,54.73514008522034,7.058984279632568,6.8766655921936035)

rekap = data.frame(metode,
		   nilai = round(nilai,5),
		   runtime = round(runtime,3))
```

```{r,echo=FALSE,fig.align='center',fig.cap="Rekap Runtime Soal I",fig.retina=10}
rekap %>%
  ggplot(aes(x = reorder(-metode,runtime),
	     y = runtime)) +
  geom_col(fill = "steelblue",
	   width = .7) +
  geom_label(aes(label = round(runtime,3)),size = 1.25) +
  coord_flip()
```
